Sketch of DP - Bayesian Inference

### 2018-07-17 main-sketch.tex
section 3 pass

% \section{Baseline Approach - Laplace Mechanism}
% \label{sec_lap}
% Our baseline approach come from the algorithm designed by \citet{zhang2016differential} that adding Laplace noise (\citet{dwork2014algorithmic}) to posterior parameters to preserve privacy. They perturbed the parameter updates of $\betad$ distribution from Bayesian inference and truncated to rule out invalid $\betad$ parameters to get the protected posteriors. Furthermore, we extend their algorithm to the case of $m$ dimensional Dirichlet distributions, where we add $(m-1)$ i.i.d. Laplace noises $\{Lap_1 , Lap_2, \cdots, Lap_{m-1} \}$ and truncate in the same way. 
% %where $Lap_i = floor(Y)$, $Y \sim Lap(\frac{2}{\epsilon})$. 
% The private posterior is $\dirichlet(\valpha + \Delta \valpha')$, where $\Delta \valpha'$ is the perturbed parameter updates.

\section{Our Approach - Exponential Mechanism with Smooth Sensitivity}
\label{sec_smoo}
Given a prior distribution $\betad(\alpha, \beta)$, depending on the dataset $\dataobs$, the posterior distribution will be one in the following set:
$$
% \subsection{Algorithm Setting up}
We define a new mechanism $\hexpmech(x)$ which is similar to the exponential mechanism where we use $\mathcal{R}$ as the set $\betaset$ of beta distributions with integer parameters summing up to $n+2$, as scoring function we use the Hellinger distance from $\bysinfer(x)$, i.e. $\hlg(\bysinfer(x),-)$, and we calibrate the noise to the smooth sensitivity~\cite{nissim2007smooth}. The only difference is in the sensitivity part, since now we use the smooth sensitivity.

\begin{definition}
\label{def_smoo}
The mechanism $\hexpmech(x)$ outputs a candidate $r \in \betaset$ with probability
\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[z=r] = \frac
{exp(\frac{-\epsilon\hlg(\bysinfer(x),r)}{2 S_\beta(x)})}
{\Sigma_{r' \in R}\ exp(\frac{-\epsilon \hlg(\bysinfer(x),r')}{2 S_\beta(x)})},
\end{equation*}
where $s_\beta(x)$ is the smooth sensitivity of $\hlg(\bysinfer(x),-)$, calculated by:
\begin{equation*}
S_{\beta}(x) = \max(\Delta_{l}\hlg(\bysinfer(x),-), \max_{y \neq x; y \in D^{n}}(\Delta_{l}\hlg(\bysinfer(y),-)\cdot e^{-\beta d(x,y)})),
\end{equation*}
where $d$ is the Hamming distance between two datasets, and $\beta =
\beta(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$. 
\end{definition}

In what follows, we will use a correspondence between the probability
 $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ of every
 $r\in\betaset$ and the probability 
 $\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
 \hlg(\bysinfer(x),r)]$ for the utility score for $r$. In particular, for every
 $r\in\betaset$ we have:
$$
\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]=
\frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
 \hlg(\bysinfer(x),r)]\Big )
$$
To see this, it is enough to notice that: $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ is proportional too $\hlg(\bysinfer(x),r)$, i.e., $u(x,z)$. We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[z = r']$. We assume the number of candidates $z \in \mathcal{R}$ that satisfy $u(z,x) = u(r,x)$ is $|r|$, we have  $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = |r| \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. Because Hellinger distance  $\hlg(\bysinfer(x),z)$ is axial symmetry, where the $\bysinfer(x)$ is the symmetry axis. It can be infer that $|z| = 2$ for any candidates, apart from the true output, i.e., $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. This parameter can be eliminate in both sides in proof.

>>>>

% \section{Baseline Approach - Laplace Mechanism}
% \label{sec_lap}
% Our baseline approach come from the algorithm designed by \citet{zhang2016differential} that adding Laplace noise (\citet{dwork2014algorithmic}) to posterior parameters to preserve privacy. They perturbed the parameter updates of $\betad$ distribution from Bayesian inference and truncated to rule out invalid $\betad$ parameters to get the protected posteriors.
% Furthermore, we extend their algorithm to the case of $m$ dimensional Dirichlet distributions, where we add $(m-1)$ i.i.d. Laplace noises $\{Lap_1 , Lap_2, \cdots, Lap_{m-1} \}$ and truncate in the same way. 
% %where $Lap_i = floor(Y)$, $Y \sim Lap(\frac{2}{\epsilon})$. 
% The private posterior is $\dirichlet(\valpha + \Delta \valpha')$, where $\Delta \valpha'$ is the perturbed parameter updates.

\section{Our Approach - Exponential Mechanism with Smooth Sensitivity}
\label{sec_smoo}
Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and a sequence of $n$ observations $\dataobs\in\{0,1\}^n$,
we define the follwing set:

\[
  \betaset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}
\]
where $\Delta\alpha$ is as defined in Section \ref{sec_background}.
Notice that $\betaset$ has $n+2$ elements, and the Bayesian Inference
process will produce an element from $\betaset$ that we denote by
$\bysinfer(\dataobs)$ -- we don't explicitely parametrize the result by the
prior,  which from now on we consider fixed and we denote it by $\bprior$.

We can now define the mechanism $\hexpmech$ which,
given in input a sequence of observations $\dataobs$, and $\epsilon>0, \delta>0$,
produces an element $r$ in $\betaset$ with probability:

\begin{equation*}
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdotS_\beta(\dataobs)})}
{\displaystyle\sum_{r\in\betaset} exp(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdotS_{\beta}(\dataobs)})}
\end{equation*}
The previous mechanism is very similar to the exponential mechanism as defined in \cite{expmech},  with $\betaset$ as range and $\hellinger(\cdot,\cdot)$ as scoring function.
The difference is that in this mechanism we don't calibrate the noise w.r.t to the global sensitivity of the scoring function but w.r.t to the smooth sensitivity
-- \citet{nissim2007smooth}-- of $\hellinger(\bysinfer(\dataobs), \cdot)$, which is :
\[
   S_{\beta}(\dataobs)=\max_{\dataobs' \neq \dataobs, \dataobs' \in \{0,1\}^{n}}\bigg \{\Delta_{l}\cdot \hellinger(\bysinfer(\dataobs'),-)\cdot e^{-\gamma\cdot d(\dataobs, \dataobs')}\bigg\}
 \]

where $d$ is the Hamming distance between two datasets, $\Delta_{l}=????$, and $\gamma =
\gamma(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$, to be determined later.
\subsection{Analysis of the mechanism}
In what follows, we will use a correspondence between the probability
 $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ of every
 $r\in\betaset$ and the probability 
 $\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
 \hlg(\bysinfer(x),r)]$ for the utility score for $r$. In particular, for every
 $r\in\betaset$ we have:
$$
\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]=
\frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
 \hlg(\bysinfer(x),r)]\Big )
$$
To see this, it is enough to notice that: $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ is proportional too $\hlg(\bysinfer(x),r)$, i.e., $u(x,z)$. We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[z = r']$. We assume the number of candidates $z \in \mathcal{R}$ that satisfy $u(z,x) = u(r,x)$ is $|r|$, we have  $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = |r| \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. Because Hellinger distance  $\hlg(\bysinfer(x),z)$ is axial symmetry, where the $\bysinfer(x)$ is the symmetry axis. It can be infer that $|z| = 2$ for any candidates, apart from the true output, i.e., $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. This parameter can be eliminate in both sides in proof.
